### 2014-03-20 manuscript.tex
Endring i introduksjon

In this paper we focus on classifying the opinion toward religious/political topics, say the Quran, in political discussion by using the lexical-based approach. 
One intuitive approach is to find both the keyword (e.g. Quran) and the words with sentiment in the sentence and classify the sentiment of the sentence based on the polarity of these sentiment words. We expect that statistically the importance of a sentiment word towards the keyword is related to the number of words between the sentiment and key word as suggested by Ding et al. \shortcite{Ding08}. Two other approaches is to automatically parse the material and either use the distance between key and sentiment word in the parse tree or develop grammatical dependence paths, see e.g. Jiang et al. \shortcite{Jiang11}. The aim of this paper is to compare the performance of a word distance method \cite{Ding08} with novel methods based on distance in parse tree and grammatical dependence paths to classify opinions in political discussions.

@@

\subsection{Parse tree method}
\label{sec:dp}
LILJA: OM PARSING

>>>>

In this paper we focus on classifying the sentiment towards
religious/political topics, say the Quran, in Norwegian political
discussion. We use a lexicon-based approach where we classify the
sentiment of a sentence based on the polarity of sentiment words in
relation to a set of target words. We expect that statistically the
importance of a sentiment word towards the keyword is related to the
number of words between the sentiment and key word as suggested by
Ding et al. \shortcite{Ding08}.  Information about the syntactic
environment of certain words or phrases has in previous work also been
shown to be useful for the task of sentiment classification
\cite{Wil:Wie:Hof:09,Jiang11}. In this work we therefore compare the
results obtained using a token-based distance measure with a novel
syntax-based distance measure obtained using dependency graphs and
further augmented with linguistically motivated syntactic patterns
expressed as dependency paths.  We furthermore present a freely
available corpus of Norwegian political discussion related to religion
and immigration, which has been manually annotated for the sentiment
expressed towards a set of target words, as well as a manually translated sentiment lexicon.

%% In this paper we focus on classifying the opinion toward religious/political topics, say the Quran, in political discussion by using the lexical-based approach. One intuitive approach is to find both the keyword (e.g. Quran) and the words with sentiment in the sentence and classify the sentiment of the sentence based on the polarity of these sentiment words. We expect that statistically the importance of a sentiment word towards the keyword is related to the number of words between the sentiment and key word as suggested by Ding et al. \shortcite{Ding08}. Two other approaches is to automatically parse the material and either use the distance between key and sentiment word in the parse tree or develop grammatical dependence paths, see e.g. Jiang et al. \shortcite{Jiang11}. The aim of this paper is to compare the performance of a word distance method \cite{Ding08} with novel methods based on distance in parse tree and grammatical dependence paths to classify opinions in political discussions.

@@

\subsection{Parse tree method}
\label{sec:dp}
%LILJA: OM PARSING
When determining the sentiment expressed towards a specific target word, the syntactic environment of this word and how it relates to sentiment-bearing words in the context may clearly be of importance.
